Emitter Source Geolocation from Imparted Rotor Blade Modulation

### 2016-11-23 Results_new.tex
added data to tables

%azimuth error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
     200 & 76\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     200 & 45\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
     500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     500 & 51.34\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
    \end{tabular}
     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 11.5dB Noise}
    \label{tab:az_error_and_percent_11db}
\end{center}
\end{table}

@@

%azimuth error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
     200 & 76\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     200 & 45\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
     500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     500 & 51.34\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
    \end{tabular}
     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 12dB Noise}
    \label{tab:az_error_and_percent_12db}
\end{center}
\end{table}

@@

%azimuth error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
     200 & 76\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
     200 & 45\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
     500 & 78.7\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
     500 & 51.34\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
    \end{tabular}
     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 20dB Noise}
    \label{tab:az_error_and_percent_20db}
\end{center}
\end{table}

@@

% Elevation error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
     200 & 76\textdegree & \textdegree & \%  \\ \hline
     200 & 45\textdegree & \textdegree & \%  \\ \hline 
     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
     500 & 78.7\textdegree & \textdegree & \% \\ \hline
     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
    \end{tabular}
    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 11.5dB Noise}
    \label{tab:elevation_error_percent_11.5db}
\end{center}
\end{table}

@@

% Elevation error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
     200 & 76\textdegree & \textdegree & \%  \\ \hline
     200 & 45\textdegree & \textdegree & \%  \\ \hline 
     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
     500 & 78.7\textdegree & \textdegree & \% \\ \hline
     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
    \end{tabular}
    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 12dB Noise}
    \label{tab:elevation_error_percent_12db}
\end{center}
\end{table}

@@

% Elevation error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
     200 & 76\textdegree & \textdegree & \%  \\ \hline
     200 & 45\textdegree & \textdegree & \%  \\ \hline 
     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
     500 & 78.7\textdegree & \textdegree & \% \\ \hline
     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
    \end{tabular}
    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 20dB Noise}
    \label{tab:elevation_error_percent_20db}
\end{center}
\end{table}

>>>>

%azimuth error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
     200 & 76\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     200 & 45\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
     200 & 26.5\textdegree & $\pm13.5$\textdegree & $\pm15\%$  \\ \hline
     500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     500 & 51.34\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
     500 & 35.5\textdegree & $\pm22.5$\textdegree & $\pm25\%$  \\ \hline
    \end{tabular}
     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 11.5dB Noise}
    \label{tab:az_error_and_percent_11db}
\end{center}
\end{table}

@@

%azimuth error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
     200 & 76\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     200 & 45\textdegree & $\pm$13.5\textdegree & $\pm15\%$  \\ \hline 
     200 & 26.5\textdegree & $\pm13.5$\textdegree & $\pm15\%$  \\ \hline
     500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     500 & 51.34\textdegree & $\pm13.5$\textdegree & $\pm15\%$  \\ \hline 
     500 & 35.5\textdegree & $\pm22.5$\textdegree & $\pm25\%$  \\ \hline
    \end{tabular}
     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 12dB Noise}
    \label{tab:az_error_and_percent_12db}
\end{center}
\end{table}

@@

%azimuth error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
     200 & 76\textdegree & $\pm22.5$\textdegree & $\pm25\%$  \\ \hline
     200 & 45\textdegree & $\pm31.5$\textdegree & $\pm35\%$  \\ \hline 
     200 & 26.5\textdegree & $\pm59.5$\textdegree & $\pm65\%$  \\ \hline
     500 & 78.7\textdegree & $\pm13.5$\textdegree & $\pm15\%$  \\ \hline
     500 & 51.34\textdegree & $\pm40.5$\textdegree & $\pm45\%$  \\ \hline 
     500 & 35.5\textdegree & $\pm67.5$\textdegree & $\pm75\%$  \\ \hline
    \end{tabular}
     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 20dB Noise}
    \label{tab:az_error_and_percent_20db}
\end{center}
\end{table}

@@

% Elevation error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
     200 & 76\textdegree &0.5533\textdegree & 0.7284\%  \\ \hline
     200 & 45\textdegree & -0.2647\textdegree & -0.5882\%  \\ \hline 
     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
     500 & 78.7\textdegree & 0.7923\textdegree & 1.0069\% \\ \hline
     500 & 51.34\textdegree & -0.3978\textdegree & -0.7747\%  \\ \hline 
     500 & 35.5\textdegree & -3.9893\textdegree & -11.2255\%  \\ \hline
    \end{tabular}
    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 11.5dB Noise}
    \label{tab:elevation_error_percent_11.5db}
\end{center}
\end{table}

@@

% Elevation error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
     200 & 76\textdegree & 0.6966\textdegree & 0.9170\%  \\ \hline
     200 & 45\textdegree & -2.3497\textdegree & -5.2215\%  \\ \hline 
     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
     500 & 78.7\textdegree & 0.8916\textdegree & 1.1331\% \\ \hline
     500 & 51.34\textdegree & -4.8613\textdegree & -9.4687\%  \\ \hline 
     500 & 35.5\textdegree & 7.8398\textdegree & 22.0606\%  \\ \hline
    \end{tabular}
    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 12dB Noise}
    \label{tab:elevation_error_percent_12db}
\end{center}
\end{table}

@@

% Elevation error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
     200 & 76\textdegree & -9.6248\textdegree & -12.6703\%  \\ \hline
     200 & 45\textdegree & 7.8795\textdegree & 17.5099\%  \\ \hline 
     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
     500 & 78.7\textdegree & 1.3260\textdegree & 1.6851\% \\ \hline
     500 & 51.34\textdegree & 4.5056\textdegree & 8.7760\%  \\ \hline 
     500 & 35.5\textdegree & 20.8592\textdegree & 58.6959\%  \\ \hline
    \end{tabular}
    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 20dB Noise}
    \label{tab:elevation_error_percent_20db}
\end{center}
\end{table}
